Time Series Analysis of Chaotic Dynamical Systems with Recurrent Neural Networks

### 2019-04-17 doc/paper/paper.tex
formatting

\begin{equation}
(\theta_1, \theta_2, \omega_1, \omega_2) 
= (4.66648088, 4.29820501,
8.01585663 \times 10^{-4}, 3.71175422 \times 10^{-3}).
\end{equation}
In this case, we
need $\theta_1$ large enough that the system is chaotic, but the rest of
the parameters were chosen randomly (with rotational velocities close to
zero). The resulting Lyapunov Exponent is $0.60074$. 
Like the Lorenz, the differences between time points
were used to train the ESN since the ESN was showing poor results
otherwise. As the pendulum kept looping the center, $\theta_1$ and 
$\theta_2$ kept growing; this shouldn't be an issue, but using
the differences keeps the system variables in a closer range.

>>>>

\begin{equation}
(\theta_1, \theta_2, \omega_1, \omega_2) 
= (4.66648088, 4.29820501,
8.01585663 \times 10^{-4}, 3.71175422 \times 10^{-3}).
\end{equation}

In this case, we need $\theta_1$ large enough that the system is chaotic, but
the rest of the parameters were chosen randomly (with rotational velocities
close to zero). The resulting Lyapunov Exponent is $0.60074$. Like the
Lorenz, the differences between time points were used to train the ESN since
the ESN was showing poor results otherwise. As the pendulum kept looping the
center, $\theta_1$ and $\theta_2$ kept growing; this shouldn't be an issue,
but using the differences keeps the system variables in a closer range.
